\documentclass{resume} % Use the custom resume.cls style

\usepackage{multicol}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage[a4paper, margin=0.2in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Tushar Basak} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 8299312126 \\ Delhi, India} 
\address{\href{mailto:tushar.basak@yahoo.com}{Mail: tushar.basak@yahoo.com} \\ 
\href{https://bit.ly/basaklinkedin}{LinkedIn: tusharbasak97} \\ \href{https://bit.ly/basakwebsite}{Portfolio: bit.ly/basakwebsite}}

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{OBJECTIVE}

{Technically adept, detail-oriented, and goal-driven professional with a solid foundation in cybersecurity and risk management. Experienced in identifying vulnerabilities, performing penetration testing, and implementing advanced security measures to protect organizational assets. Proficient in threat analysis, incident response, and compliance monitoring. Skilled in conducting security audits, leveraging SIEM tools, and designing comprehensive defense strategies against evolving cyber threats. Adept at collaborating with cross-functional teams, clients, and stakeholders to meet organizational security objectives. Bilingual in English and Japanese, with exceptional communication skills and a proactive approach to problem-solving. Areas of expertise include:}

\vspace{3mm}
\begin{center}
    Vulnerability Assessment and Management | Penetration Testing | Incident Response and Forensics \\
    Threat Intelligence | Security Auditing | Risk Assessment | Network and System Hardening
\end{center}

\end{rSection}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

\textbf{Cybersecurity Trainee} \href{https://bit.ly/basakstrive}{View} \hfill May 2024 - Sept 2024\\
Tata Strive $|$ SAP India \hfill \textit{Anand, Gujarat}
 \begin{itemize}
    \item Conducted practical and hands-on training in \textbf{ethical hacking, SOC, and network security}.
    \item Gained a good understanding of \textbf{network protocols} such as \textbf{TCP/IP, HTTP, and SSL}.
    % \item Performed \textbf{OSINT (Open Source Intelligence)} techniques and tools.
    \item Assisted in \textbf{vulnerability research} to discover new software vulnerabilities.
    \item Developed skills in \textbf{incident response, threat analysis and mitigation}.
    \item Utilized security tools like \textbf{Nmap, Burp Suite, Wireshark}, and other \textbf{tools}.
    % \item Learned about \textbf{web application hacking} and \textbf{OWASP Top 10 Security Issues}.
    \item Understood browser security concepts including \textbf{Content Security Policy}.
    % \item Built and automated \textbf{Red Teaming workflows} and security tools.
 \end{itemize}
% \textbf{Cybersecurity Analyst} \hfill July 2024\\
% Tata Group's Forage \hfill \textit{Remote}
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Completed a job simulation involving identity and access management (IAM) for Tata Consultancy Services, collaborating with a Cybersecurity Consulting team.
%      \item Acquired expertise in IAM principles, cybersecurity best practices, and strategic alignment with business objectives.
%     \item Delivered comprehensive documentation and presentations, showcasing the ability to communicate complex technical concepts effectively.
%  \end{itemize}

\vspace{6mm}
\textbf{Desktop Support Engineer} \hfill Mar 2023 - May 2024\\
Secure Life HR Service Private Ltd. \hfill \textit{New Delhi}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Provided technical support for Windows operating systems, ensuring smooth and efficient desktop, laptop, and printer operations.
     \item Installed, configured, and maintained hardware components such as printers, scanners, and other office peripherals.
     \item Performed troubleshooting for network connectivity issues, including LAN/WAN setup and configurations.
     \item Managed network security by implementing antivirus programs and firewall settings.
     \item Provided remote troubleshooting support and clear instructions to clients for quick resolution of technical issues.
     \item Assisted in the repair and maintenance of desktops and laptops, including hardware upgrades and replacements.
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{TOOLS \& SKILLS}
\begin{itemize}
    \item \textbf{Cybersecurity:} Vulnerability scanning, penetration testing, SIEM tools, threat intelligence
    \item \textbf{Incident Response:} Log analysis, forensic investigation, malware analysis, and mitigation strategies
    \item \textbf{Networking:} Network security, firewall configuration, LAN/WAN troubleshooting, packet analysis
    \item \textbf{System Security:} Endpoint protection, hardening Windows and Linux environments
    \item \textbf{Technical Support:} Providing security awareness training, troubleshooting security issues, IT service support
    \item \textbf{Programming and Scripting:} Python for automation, Bash scripting for security tasks
\end{itemize}
\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

{\bf Master of Computer Applications}, Manipal University, Jaipur \hfill {May 2021 - July 2023}\\
\textbf{CGPA: 8.92}

{\bf Bachelor of Science}, Swami Vivekananda Subharti University, Meerut \hfill {July 2017 - Dec 2019}\\
\textbf{Percentage: 68.5\%}

% {\bf Intermediate}, St. Aloysius High School, Kanpur \hfill {May 2015 - May 2016}\\
% \textbf{Percentage: 60\%}

% {\bf High School}, St. Aloysius High School, Kanpur \hfill {May 2013 - May 2014}\\
% \textbf{Percentage: 72\%}

\end{rSection}
%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------
\begin{rSection}{CERTIFICATIONS}
\begin{itemize}
    \item Tata Group - Cybersecurity Analyst Job Simulation \hfill \href{https://forage-uploads-prod.s3.amazonaws.com/completion-certificates/Tata/gmf3ypEXBj2wvfQWC_Tata%20Group_PynkGwAqrec2LCHy3_1719852016860_completion_certificate.pdf}{View}\\
    \textbf{Forage} \hfill July 2024
    \item GATE CS/IT + DA \hfill \href{https://}{Applied}\\
    \textbf{IIT Roorkee} \hfill Feb 2025
\end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\begin{itemize}
    \item \textbf{Completion of 30+ Labs on PortSwigger and 5+ Machines on TryHackMe:} {Completed over 30 hands-on labs on \textit{PortSwigger}, mastering a wide range of web vulnerabilities, including \textit{SQL Injection}, \textit{Cross-Site Scripting (XSS)}, \textit{Cross-Site Request Forgery (CSRF)}, \textit{Clickjacking}, \textit{XML External Entity (XXE) Injection}, \textit{Server-Side Request Forgery (SSRF)}, \textit{Path Traversal}, \textit{HTTP Request Smuggling}, \textit{OS Command Injection}, and more. Gained expertise in identifying and exploiting modern vulnerabilities in web applications, \textit{APIs}, and \textit{GraphQL}. Additionally, solved 5+ real-world machines on \textit{TryHackMe}, focusing on topics such as privilege escalation, penetration testing, and secure configurations.}
    \item \textbf{Penetration Testing on Metasploitable2:} {Performed ethical hacking and exploitation of the intentionally vulnerable \textit{Metasploitable} machine within a virtual lab environment. Conducted reconnaissance using tools like \textit{Nmap}, exploited vulnerabilities using the \textit{Metasploit Framework}, and demonstrated techniques such as \textit{SQL Injection}, privilege escalation, and exploitation of misconfigured services. Documented the attack methodology and proposed actionable security measures to secure similar systems.}
\end{itemize}
\end{rSection}



%----------------------------------------------------------------------------------------
%	LEADERSHIP SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership}
\textbf{City President} \hfill Jan 2023 - Dec 2023\\
BloodConnect Foundation \hfill \textit{Kanpur, UP}
\begin{itemize}[noitemsep]
    \item Spearheaded a 2-tier team of 20+ students, efficiently managed a budget of INR 2.5 LPA, and improved helpline processes for enhanced customer satisfaction.
    \item Organized 20+ blood donation camps, collecting 1K+ units of blood, impacting 3K+ lives, and inspiring campus community participation.
    \item Demonstrated leadership, budget management, process improvement, and community engagement.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% \section*{\textcolor{white}{\fontsize{1}{1.2}\selectfont This is a section with white text and font size 1 point}}

% \textcolor{white}{\fontsize{1}{1.2}\selectfont
% web application
% web
% tcp/ip
% ssl
% self
% saas
% research
% r
% programming language
% open source
% li
% less
% kubernetes
% issues
% innovation
% http
% go
% founder
% engineer
% docker
% cloud
% software
% security
% python
% programming
% product
% documentation
% computer science
% }


%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\
%----------------------------------------------------------------------------------------

\end{document}
